### 2010-10-02 annualreports/2010/directorsreport.tex
Fixes. This is the version submitted to Companies House

@@

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.
\pagebreak

>>>>

\subsection{Corporation Tax}
As all members of the London Hackspace are also members of the company, we believe
that we are trading under the mutual trading/membership associations exemption from corporation tax.

As such, we believe that the Hackspace Foundation is not liable for any significant amount of
corporation tax in this financial year.

@@

This report has been prepared in accordance with the special provisions relating to small companies within Part 15 of the Companies Act 2006.

Approved by the Board for issue on 6\superscript{th} September 2010.
\vspace{48pt}

Russell Garrett \\
{\bf Director} \\
Company Number: 06807563

### 2010-10-02 annualreports/2010/notes.tex
Fixes. This is the version submitted to Companies House

\section {Notes to the Financial Statements}
\begin{enumerate}
    \item {\bf Accounting policies}
    \begin{enumerate}
        \item {\bf Accounting convention} \\
                The financial statements are prepared under the 
            historical cost convention and in accordance with the Financial Reporting 
            Standard for Smaller Entities (effective April 2008).
        \item {\bf Compliance with accounting standards} \\
            The financial statements are prepared in accordance with applicable United
            Kingdom Accounting Standards (United Kingdom Generally Accepted Accounting
            Practice), which have been applied consistently throughout the period.
        \item {\bf Turnover} \\
            Turnover represents amounts receivable for services.
        \item {\bf Tangible fixed assets and depreciation} \\
            Tangible fixed assets are stated at cost less depreciation. Depreciation is
            provided at rates calculated to write off the cost less estimated residual
            value of each asset over its expected useful life, as follows: \\
            \begin{tabular}{  l  p{6.5cm} }
                \toprule
                Fixtures \& Fittings & Over 3 years at 33\% per annum on a straight line basis \\
                Plant \& Machinery & Over 3 years at 33\% per annum on a straight line basis \\
                \bottomrule
            \end{tabular}
    \end{enumerate}
\end{enumerate}

>>>>

\section {Notes to the Financial Statements}
\begin{enumerate}
    \item {\bf Accounting policies}
    \begin{enumerate}
        \item {\bf Accounting convention} \\
                The financial statements are prepared under the 
            historical cost convention and in accordance with the Financial Reporting 
            Standard for Smaller Entities (effective April 2008).
        \item {\bf Compliance with accounting standards} \\
            The financial statements are prepared in accordance with applicable United
            Kingdom Accounting Standards (United Kingdom Generally Accepted Accounting
            Practice), which have been applied consistently throughout the period.
        \item {\bf Turnover} \\
            Turnover represents amounts receivable for services.
        \item {\bf Tangible fixed assets and depreciation} \\
            Tangible fixed assets are stated at cost less depreciation. Depreciation is
            provided at rates calculated to write off the cost less estimated residual
            value of each asset over its expected useful life, as follows: \\[6pt]
            \begin{tabular}{  l  p{6.5cm} }
                \toprule
                Fixtures \& Fittings & Over 3 years at 33\% per annum on a straight line basis \\
                Plant \& Machinery & Over 3 years at 33\% per annum on a straight line basis \\
                \bottomrule
            \end{tabular}
    \end{enumerate}
\end{enumerate}
